### 2020-04-04 reports/thesis/chapters/1_literatureReview.tex
Final revise
Corrections

Imaging using x-rays \citep{rontgen1896on} have been used in the medical field. In x-ray computed tomography \citep{cormack1973reconstruction, hounsfield1973computerized, hounsfield1980computed}, the patient has an x-ray image taken at multiple angles. These x-ray images are used to reconstruct what was taken in 3D to make a diagnostic.

@@

Fused deposition modelling is another liquid-based AM technology. A jetting head, or nozzle, deposit the molten material onto a platform or on top of the previous layer. The material is usually plastic in the form of a thin filament. It is heated to just above its melting points, typically \SI{1}{\degreeCelsius} \citep{crump1992apparatus}, so that it cools down within \SI{0.1}{\second} \citep{kruth1991material}. The platform moves, and controlled by a computer, in the $xy$-plane, or left to right and front to back, to produce a layer. The jetting head can move in the $z$-axis, or up and down, to manufacture the next layer. In the original patent by \cite{crump1992apparatus}, the thickness can be as thin as 0.000\,1 inches (\SI{0.003}{\milli\metre}).

@@

After attenuation, the x-ray photons are detected by the x-ray detector. The detectors used in XCT are typically flatbed scanners made up of a scintillator material \citep{curran1953luminescence, greskovich1997ceramic} and photodiodes. The x-ray photons interact with the scintillator material and produce visible light pluses \citep{rossner1993conversion}. These pulses are detected by photodiodes and converted into an electrical signal \citep{nikl2006scintillation, ren2018tutorial}. The electrical signal can be a quantum counter, counting the number of photons detected, or an energy integrating detector, adding up all of the energies of each detected photon \citep{nikl2006scintillation, whiting2006properties, kruth2011computed, ren2018tutorial}. The electrical signals are subject to sampling and quantisation to store these signals as an image \citep{cierniak2011x}. This image is known as a projection.

@@

XCT can be used to measuring lengths and distances, making it useful for measuring the dimensions of AM objects internally and externally. \emph{Nikon} offer products and services for XCT including features such as direct comparison to the CAD model \citep{nikon2015microfocus, nikon2018mct225} and automated production line inspection \citep{nikon2015inline, nikon2018automated}.

@@

Errors due to beam hardening can occur. Low energy photons are more likely to be absorbed or scattered, which causes a few millimetres of the surface of the object to absorb or scatter more photons than the interior. This can cause artefacts \citep{sun2016applications} such as flat surfaces to be barrelled and edges rounded off \citep{kruth2011computed}. Beam hardening can be tackled by eliminating the low energy photons by placing a filter, a thin metal plate, in front of the x-ray tube \citep{welkenhuyzen2009industrial}, for example, copper. Figure \ref{fig:literature_hardening} shows an example of reconstruction with and without a filter. Without the filter, the outer perimeter appears less dense than it should be.  A filter reduces the rate of photon emission but this can be compensated by increasing the exposure time \citep{kruth2011computed}. Early reconstruction algorithms ignored beam hardening but modern methods can take beam hardening into account \citep{elbakri2001statistical, sun2016applications}.

>>>>

Imaging using x-rays \citep{rontgen1896on} has been used in the medical field. In x-ray computed tomography \citep{cormack1973reconstruction, hounsfield1973computerized, hounsfield1980computed}, the patient has an x-ray image taken at multiple angles. These x-ray images are used to reconstruct what was taken in 3D to make a diagnostic.

@@

Fused deposition modelling is another liquid-based AM technology. A jetting head, or nozzle, deposits the molten material onto a platform or on top of the previous layer. The material is usually plastic in the form of a thin filament. It is heated to just above its melting points, typically \SI{1}{\degreeCelsius} \citep{crump1992apparatus}, so that it cools down within \SI{0.1}{\second} \citep{kruth1991material}. The platform moves, and controlled by a computer, in the $xy$-plane, or left to right and front to back, to produce a layer. The jetting head can move in the $z$-axis, or up and down, to manufacture the next layer. In the original patent by \cite{crump1992apparatus}, the thickness can be as thin as 0.000\,1 inches (\SI{0.003}{\milli\metre}).

@@

After attenuation, the x-ray photons are detected by the x-ray detector. The detectors used in XCT are typically flatbed scanners made up of a scintillator material \citep{curran1953luminescence, greskovich1997ceramic} and photodiodes. The x-ray photons interact with the scintillator material and produce visible light pulses \citep{rossner1993conversion}. These pulses are detected by photodiodes and converted into an electrical signal \citep{nikl2006scintillation, ren2018tutorial}. The electrical signal can be a quantum counter, counting the number of photons detected, or an energy integrating detector, adding up all of the energies of each detected photon \citep{nikl2006scintillation, whiting2006properties, kruth2011computed, ren2018tutorial}. The electrical signals are subject to sampling and quantisation to store these signals as an image \citep{cierniak2011x}. This image is known as a projection.

@@

XCT can be used to measure lengths and distances, making it useful for measuring the dimensions of AM objects internally and externally. \emph{Nikon} offer products and services for XCT including features such as direct comparison to the CAD model \citep{nikon2015microfocus, nikon2018mct225} and automated production line inspection \citep{nikon2015inline, nikon2018automated}.

@@

Errors due to beam hardening can occur. Low energy photons are more likely to be absorbed or scattered, which causes a few millimetres of the surface of the object to absorb or scatter more photons than the interior. This can cause artefacts \citep{sun2016applications} such as flat surfaces to be barrelled and edges rounded off \citep{kruth2011computed}. Beam hardening can be tackled by eliminating the low energy photons by placing a filter, a thin metal plate, in front of the x-ray tube \citep{welkenhuyzen2009industrial}, for example, copper. Figure \ref{fig:literature_hardening} shows an example of reconstruction with and without a filter. Without the filter, the interior of the object appears less dense than it should be.  A filter reduces the rate of photon emission but this can be compensated by increasing the exposure time \citep{kruth2011computed}. Early reconstruction algorithms ignored beam hardening but modern methods can take beam hardening into account \citep{elbakri2001statistical, sun2016applications}.

### 2020-04-04 reports/thesis/chapters/2_dataCollection.tex
Corrections

Let $S_{x,y}(P)$ be the greyscale projection when exposed to x-rays produced by an x-ray tube with power $P$ for some fixed time exposure $\tau$. $S_{x,y}(P)$ may be averaged over replications. Let $x=1,2,3,\dotsc, W$ and $y=1,2,3,\dotsc,H$. Let $N_{x,y}$ be the obtained projection of the test sample when exposed to x-rays produced by an x-ray tube with power $P_\text{proj}$ for some fixed time exposure $\tau$. The black and white images can be expressed as $\text{black}_{x,y}=S_{x,y}(0)$ and $\text{white}_{x,y}=S_{x,y}(P_\text{proj})$ respectively. The power was varied by fixing the potential difference and varying the current of the x-ray tube.

@@

\begin{figure}
  \centerline{
    \begin{subfigure}[b]{\textwidth}
      \includegraphics[width=\subSize]{../figures/data/oddEvenPlot1_null.eps}
      \includegraphics[width=\subSize]{../figures/data/oddEvenPlot2_null.eps}
      \caption{No shading correction}
    \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{\textwidth}
      \includegraphics[width=\subSize]{../figures/data/oddEvenPlot1_bw.eps}
      \includegraphics[width=\subSize]{../figures/data/oddEvenPlot2_bw.eps}
      \caption{BW shading correction}
    \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{\textwidth}
      \includegraphics[width=\subSize]{../figures/data/oddEvenPlot1_linear.eps}
      \includegraphics[width=\subSize]{../figures/data/oddEvenPlot2_linear.eps}
      \caption{linear shading correction}
    \end{subfigure}
  }
  \caption{Left shows the profile plot of an \texttt{AbsNoFilter} black image at $(879,y)$ using various shading corrections. Right shows two curves for odd and even $y$.}
  \label{fig:data_oddEven}
\end{figure}

@@

For each power, the within and between pixel variance was calculated. Let $U_{x,y}^{(j)}(P)$ be the shading corrected greyscale image in the test set with power $P$ for $j=1,2,\dotsc,m$ replicates. The within and between pixel variance are
\begin{equation}
s_\mathrm{w}^2(P)=\dfrac{1}{WH(m-1)}
  \sum_{x=1}^{W}\sum_{y=1}^{H}\sum_{j=1}^{m}
  \left(
    U_{x,y}^{(j)}(P) - \overline{U}_{x,y}(P)
  \right)^2
\end{equation}
and
\begin{equation}
s_\mathrm{b}^2(P)=\dfrac{m}{WH-1}
  \sum_{x=1}^{W}\sum_{y=1}^{H}
  \left(
    \overline{U}_{x,y}(P) - \overline{U}(P)
  \right)^2
\end{equation}
respectively where
\begin{equation}
  \overline{U}_{x,y}(P) = \dfrac{1}{m}\sum_{j=1}^{m}U_{x,y}^{(j)}(P)
\end{equation}
and
\begin{equation}
  \overline{U}(P) = \dfrac{1}{WH}\sum_{x=1}^{W}\sum_{y=1}^{H}\overline{U}_{x,y}(P)
  \ .
\end{equation}
In this specific experiment, $W=2000$, $H=2000$ and $m=19$. The $F$ statistic is
\begin{equation}
F(P)=\dfrac{s_\mathrm{b}^2(P)}{s_\mathrm{w}^2(P)}
\end{equation}
and it should be about one if the within and between pixel variances are similar. The experiment was repeated 100 times by reallocating the training and test set.

\begin{figure}[p]
  \centering
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/ShadingCorrectionAnovaAbsNoFilter_null.eps}
      \caption{No shading correction}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/ShadingCorrectionAnovaAbsNoFilter_bw.eps}
      \caption{BW shading correction}
    \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/ShadingCorrectionAnovaAbsNoFilter_linear.eps}
      \caption{Linear shading Correction}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/ShadingCorrectionAnovaAbsNoFilter_FStatistic.eps}
      \caption{$F$ statistic}
    \end{subfigure}
  }
  \caption{One randomly selected greyscale image from each power was used to train the shading correction which was then applied to the remaining of the greyscale projections. The within and between pixel variance were estimated and used to calculate a $F$ statistic for each power. The experiment was repeated by reselecting the greyscale projections used for training the shading correction.  The boxplots represent the 100 repeats. The \texttt{AbsNoFilter} dataset was used here.}
  \label{fig:data_anovaAbsNoFilter}
\end{figure}

\begin{figure}[p]
  \centering
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/ShadingCorrectionAnovaAbsFilter_null.eps}
      \caption{No shading correction}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/ShadingCorrectionAnovaAbsFilter_bw.eps}
      \caption{BW shading correction}
    \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/ShadingCorrectionAnovaAbsFilter_linear.eps}
      \caption{Linear shading Correction}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/ShadingCorrectionAnovaAbsFilter_FStatistic.eps}
      \caption{$F$ statistic}
    \end{subfigure}
  }
  \caption{One randomly selected greyscale image from each power was used to train the shading correction which was then applied to the remaining of the greyscale projections. The within and between pixel variance were estimated and used to calculate a $F$ statistic for each power. The experiment was repeated by reselecting the greyscale projections used for training the shading correction.  The boxplots represent the 100 repeats. The \texttt{AbsFilter} dataset was used here.}
  \label{fig:data_anovaAbsFilter}
\end{figure}

>>>>

Let $S_{x,y}(P)$ be the greyscale projection when exposed to x-rays produced by an x-ray tube with power $P$ for some fixed time exposure $\tau$. The projection, $S_{x,y}(P)$, may be averaged over replications. Let $x=1,2,3,\ldots, W$ and $y=1,2,3,\ldots,H$. Let $N_{x,y}$ be the obtained projection of the test sample when exposed to x-rays produced by an x-ray tube with power $P_\text{proj}$ for some fixed time exposure $\tau$. The black and white images can be expressed as $\text{black}_{x,y}=S_{x,y}(0)$ and $\text{white}_{x,y}=S_{x,y}(P_\text{proj})$ respectively. The power was varied by fixing the potential difference and varying the current of the x-ray tube.

@@

\begin{figure}
  \centerline{
    \begin{subfigure}[b]{\textwidth}
      \includegraphics[width=\subSize]{../figures/data/oddEvenPlot1_null.eps}
      \includegraphics[width=\subSize]{../figures/data/oddEvenPlot2_null.eps}
      \caption{No shading correction}
    \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{\textwidth}
      \includegraphics[width=\subSize]{../figures/data/oddEvenPlot1_bw.eps}
      \includegraphics[width=\subSize]{../figures/data/oddEvenPlot2_bw.eps}
      \caption{BW shading correction}
    \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{\textwidth}
      \includegraphics[width=\subSize]{../figures/data/oddEvenPlot1_linear.eps}
      \includegraphics[width=\subSize]{../figures/data/oddEvenPlot2_linear.eps}
      \caption{Linear shading correction}
    \end{subfigure}
  }
  \caption{Left shows the profile plot of an \texttt{AbsNoFilter} black image at $(879,y)$ using various shading corrections. Right shows two curves for odd and even $y$.}
  \label{fig:data_oddEven}
\end{figure}

@@

For each power, the within and between pixel variance was calculated. Let $U_{x,y}^{(j)}(P)$ be the shading corrected greyscale image in the test set with power $P$ for $j=1,2,\ldots,m$ replicates. The within and between pixel variance are
\begin{equation}
s_\mathrm{w}^2(P)=\dfrac{1}{WH(m-1)}
  \sum_{x=1}^{W}\sum_{y=1}^{H}\sum_{j=1}^{m}
  \left(
    U_{x,y}^{(j)}(P) - \overline{U}_{x,y}(P)
  \right)^2
\end{equation}
and
\begin{equation}
s_\mathrm{b}^2(P)=\dfrac{m}{WH-1}
  \sum_{x=1}^{W}\sum_{y=1}^{H}
  \left(
    \overline{U}_{x,y}(P) - \overline{U}(P)
  \right)^2
\end{equation}
respectively where
\begin{equation}
  \overline{U}_{x,y}(P) = \dfrac{1}{m}\sum_{j=1}^{m}U_{x,y}^{(j)}(P)
\end{equation}
and
\begin{equation}
  \overline{U}(P) = \dfrac{1}{WH}\sum_{x=1}^{W}\sum_{y=1}^{H}\overline{U}_{x,y}(P)
  \ .
\end{equation}
In this specific experiment, $W=2000$, $H=2000$ and $m=19$. The $F$ statistic is
\begin{equation}
F(P)=\dfrac{s_\mathrm{b}^2(P)}{s_\mathrm{w}^2(P)}
\end{equation}
and it should be about one if the within and between pixel variances are similar. The experiment was repeated 100 times by reallocating the training and test set.

\begin{figure}[p]
  \centering
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/ShadingCorrectionAnovaAbsNoFilter_null.eps}
      \caption{No shading correction}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/ShadingCorrectionAnovaAbsNoFilter_bw.eps}
      \caption{BW shading correction}
    \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/ShadingCorrectionAnovaAbsNoFilter_linear.eps}
      \caption{Linear shading correction}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/ShadingCorrectionAnovaAbsNoFilter_FStatistic.eps}
      \caption{$F$ statistic}
    \end{subfigure}
  }
  \caption{One randomly selected greyscale image from each power was used to train the shading correction which was then applied to the remaining of the greyscale projections. The within and between pixel variance were estimated and used to calculate a $F$ statistic for each power. The experiment was repeated by reselecting the greyscale projections used for training the shading correction.  The boxplots represent the 100 repeats. The \texttt{AbsNoFilter} dataset was used here.}
  \label{fig:data_anovaAbsNoFilter}
\end{figure}

\begin{figure}[p]
  \centering
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/ShadingCorrectionAnovaAbsFilter_null.eps}
      \caption{No shading correction}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/ShadingCorrectionAnovaAbsFilter_bw.eps}
      \caption{BW shading correction}
    \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/ShadingCorrectionAnovaAbsFilter_linear.eps}
      \caption{Linear shading correction}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/ShadingCorrectionAnovaAbsFilter_FStatistic.eps}
      \caption{$F$ statistic}
    \end{subfigure}
  }
  \caption{One randomly selected greyscale image from each power was used to train the shading correction which was then applied to the remaining of the greyscale projections. The within and between pixel variance were estimated and used to calculate a $F$ statistic for each power. The experiment was repeated by reselecting the greyscale projections used for training the shading correction.  The boxplots represent the 100 repeats. The \texttt{AbsFilter} dataset was used here.}
  \label{fig:data_anovaAbsFilter}
\end{figure}
